%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Pranav Goyanka} \\ \vspace{1pt}
    \small Boston, MA $|$
    \small 774-284-6311 $|$ \href{mailto:pgoyanka@gmail.com}{\underline{pgoyanka@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/pranavgoyanka/}{\underline{linkedin.com/in/pranavgoyanka/}} $|$
    \href{https://github.com/pranavgoyanka/}{\underline{github.com/pranavgoyanka}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Boston University}{Boston, MA}
      {MS in Computer Science $|$ GPA: 3.78/4.00 }{Sep 2023 -- Dec 2024}
      \resumeItem{Courses: Principles of Machine Learning, Distributed Systems, Tools for Data Science}
    \resumeSubheading
      {Thapar Institute of Engineering and Technology}{Patiala, India}
      {BE in Electronics and Communication Engineering $|$ CGPA: 8.84/10.00 }{Jul 2017 -- Jun 2021}
      \resumeItem{Courses: Data Structures and Algorithms, Operating Systems}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Golang, Typescript, Javascript, C++, Python, Java,  SQL, HTML/CSS} \\
     \textbf{Frameworks}{: Pytorch, TensorFlow, Node.js, Socket.IO, Websocket, OpenTelemetry } \\
     \textbf{Tools \& Libraries}{: Redis, scikit-learn, AWS, RESTful API, Git, Linux} \\
     % \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     % \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
          {Teaching Assistant and Course Designer}{Jan 2024 -- Present}
          {Boston University}{Boston, MA}
          \resumeItemListStart
      \resumeItem{ Assisted in CS350 - Distributed Systems course, conducting weekly lab sessions and office hours.}
      %  \resumeItem{ Held weekly lab sessions and office hours, helping students build distributed systems using Golang.}
       \resumeItem{ Designed programming assignments and grading infrastructure for the course.}
       \resumeItem{ Implemented the OmniPaxos consensus protocol in Golang to overcome Raft's partial connectivity limitations.}
          \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer}{Oct 2022 -- Jul 2023}
      {Mobile Premier League}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{ Engineered backend systems and centralized libraries for NodeJS based server-authoritative games.}
  \resumeItem{ Optimised infrastructure utilization and monitoring via centralized libraries and OpenTelemetry integration, resulting in a 40\% reduction in infrastructure costs.}
   \resumeItem{ Improved existing matchmaking systems, leading to a 70\% increase in user engagement and retention.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Development Engineer}{Aug 2021 - Oct 2022}
      {Amadeus Software Labs}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built a Splunk Dashboard for Functional Monitoring and FMEA, cutting manual tasks by 50\%.}
        \resumeItem{Resolved daily incidents promptly in the C++ based Back Office Tool, resulting in a 40\% incident reduction.}
        \resumeItem{Rectified malfunctioning SQL database purge scripts, reducing disk space usage over 90\%.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Software Engineering Intern}{Jan 2021 - May 2021}
      {Amadeus Software Labs}{Bangalore, India}
      \resumeItemListStart
       \resumeItem{Created 'Chatbot as a Service', a modular framework to reduce chatbot development effort by more than 50\%.}
         \resumeItem{Developed standalone Java libraries for Google Dialogflow and IBM Watson’s NLP APIs, and MongoDB.}
        \resumeItem{Released the libraries to the internal Maven Repository, used by other chatbot teams at Amadeus.}
    \resumeItemListEnd

  % Not using SubSubheading because Workday doesn't parse it properly
  %  \resumeSubSubheading
  %   {Software Engineering Intern}{Jan 2021 - May 2021}
  %   \resumeItemListStart
  %      \resumeItem{Created 'Chatbot as a Service', a modular framework to reduce chatbot development effort by more than 50\%.}
  %        \resumeItem{Developed standalone Java libraries for Google Dialogflow and IBM Watson’s NLP APIs, and MongoDB.}
  %       \resumeItem{Released the libraries to the internal Maven Repository, used by other chatbot teams at Amadeus.}
  %   \resumeItemListEnd

      \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/archive/2020/projects/5793865656696832}{\underline{\textbf{Student Developer}}}}{Jun 2020 - Aug 2020}
      {Google Summer of Code at AOSSIE}{Remote}
      \resumeItemListStart
        \resumeItem{Contributed to the 'Social Street Smart' project aimed at combating fake information on the internet.}
        \resumeItem{Developed a JavaScript API\textbf{ }to detect disinformation in images using the Google Images API.}
        \resumeItem{Created and deployed serverless Machine Learning models and APIs for fake news detection.}
        \resumeItem{Migrated ML models built using Tensorflow to TFLite, making them lightweight and AWS Lambda compatible.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          { \href{https://github.com/pranavgoyanka/cs542-common-task}{\underline{\textbf{Automated Trading System}}} $|$ \emph{Python, TensorFlow, scikit-learn}}{Mar 2024 - Apr 2024}
          \resumeItemListStart
            \resumeItem{Built LSTM models to predict daily temperatures for four cities using multi-source weather data.}
            \resumeItem{Created an automated trading system with Kalshi Python API, earning \$1,887 profit.}
            \resumeItem{Collected, cleaned, and processed weather data from four sources via APIs for model training.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Fault Tolerant Key Value Store} $|$ \emph{Golang, Raft Consensus Algorithm}}{Oct 2023 - Nov 2023}
          \resumeItemListStart
            \resumeItem{Implemented the Raft distributed consensus algorithm using Go, with snapshotting support.}
            \resumeItem{Built a key value store that uses Raft as the underlying protocol.}
            \resumeItem{Tested the system against various network and node failures to ensure fault tolerance.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%

%-------------------------------------------
\end{document}
