
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
          {Teaching Assistant \& Course Designer \textnormal{\emph{$|$ Distributed Systems (CS350 \& CS351)}}}{Jan 2024 -- Present}
          {Boston University}{Boston, MA}
          \resumeItemListStart
          \resumeItem{ Implemented the OmniPaxos consensus protocol in Golang to overcome Raft's partial connectivity limitations.}
          %  \resumeItem{ Held weekly lab sessions and office hours, helping students build distributed systems using Golang.}
          \resumeItem{ Designed programming assignments and grading infrastructure for the course.}
          \resumeItem{ Assisted Prof. John Liagouris in conducting weekly lab sessions and office hours.}
          \resumeItemListEnd

    \resumeSubheading
      {Software Development Engineer}{Oct 2022 -- Jul 2023}
      {Mobile Premier League}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{ Engineered backend systems and centralized libraries for Node.js microservice based server-authoritative games.}
        \resumeItem{ Optimised infrastructure utilization and monitoring via centralized libraries and OpenTelemetry integration, resulting in a 40\% reduction in infrastructure costs.}
        \resumeItem{ Improved existing matchmaking systems, leading to a 70\% increase in user engagement and retention.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Development Engineer}{Aug 2021 - Oct 2022}
      {Amadeus Software Labs}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Built a Splunk Dashboard for Functional Monitoring and FMEA, cutting manual tasks by 50\%.}
        \resumeItem{Rectified malfunctioning SQL database purge scripts, reducing disk space usage over 90\%.}
        \resumeItem{Resolved daily incidents promptly in the C++ based Back Office Tool, resulting in a 40\% incident reduction.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Software Engineering Intern}{Jan 2021 - May 2021}
      {Amadeus Software Labs}{Bangalore, India}
      \resumeItemListStart
       \resumeItem{Created 'Chatbot as a Service', a modular framework to reduce chatbot development effort by more than 50\%.}
         \resumeItem{Developed standalone Java libraries for Google Dialogflow and IBM Watson’s NLP APIs, and MongoDB.}
        \resumeItem{Released the libraries to the internal Maven Repository, used by other chatbot teams at Amadeus.}
    \resumeItemListEnd

  % Not using SubSubheading because Workday doesn't parse it properly
  %  \resumeSubSubheading
  %   {Software Engineering Intern}{Jan 2021 - May 2021}
  %   \resumeItemListStart
  %      \resumeItem{Created 'Chatbot as a Service', a modular framework to reduce chatbot development effort by more than 50\%.}
  %        \resumeItem{Developed standalone Java libraries for Google Dialogflow and IBM Watson’s NLP APIs, and MongoDB.}
  %       \resumeItem{Released the libraries to the internal Maven Repository, used by other chatbot teams at Amadeus.}
  %   \resumeItemListEnd

      \resumeSubheading
      {\href{https://summerofcode.withgoogle.com/archive/2020/projects/5793865656696832}{\underline{\textbf{Student Developer}}}}{Jun 2020 - Aug 2020}
      {Google Summer of Code at AOSSIE}{Remote}
      \resumeItemListStart
      \resumeItem{Contributed to the project 'Social Street Smart' for combating fake information on the internet.}
      \resumeItem{Created and deployed serverless Machine Learning models, CI/CD pipelines and APIs for fake news detection.}
      \resumeItem{Migrated TensorFlow Machine Learning models to lightweight TFLite models \& deployed them to AWS Lambda.}
      \resumeItem{Developed a JavaScript API to detect disinformation in images using the Google Images API.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
